---
title: "Project"
author: "Paola Estrada Contreras"
date: "2023-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(tidyverse)
library(plotly)

```


## Is there a significant difference in the time i am scheduled to work vs the amount of time i actually work

$\mu1$: Number of hours scheduled
$\mu2$: Number of hours actually worked

$H_0: \mu1 =  \mu2$
$H_a: \mu1 \neq \mu2$ 

p-value = 0.01232

At a 0.05 signifcance level, we reject the null hypothesis. There is enough eveidence to conclude that the the number of hours scheduled vs number of hours actually worked is significantly different. 

```{r}
LexHours=read_excel("C:/Users/epaol/OneDrive/Desktop/School/Fall 2023/DATA 211/Homework/LexHours.xlsx")

LexHours

t.test(LexHours$`Hours Scheduled`, LexHours$`Actual Hours Worked`, alternative = "two.sided", paired = TRUE)

LexLong=LexHours%>%
  pivot_longer(cols = c(`Hours Scheduled`,`Actual Hours Worked`), names_to = "type", values_to = "counts")

LexLong

LexBox=LexLong%>%
  group_by(type)%>%
  ggplot(aes(x=type, y=counts))+geom_boxplot(aes(colour=type), outlier.colour = "black")+labs(x="", y="Hours")

ggplotly(LexBox)
```

